%-------------------------
% Cover Letter in Latex
% Author : Your Name
% Based off of: resume.tex by Jake Gutierrez
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{center}
    {\Huge \scshape Malcolm Kahora} \\ \vspace{1pt}
    Scotch Plains, NJ 07076 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 732-585-3225 ~ \href{mailto:malcolmkahora@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{malcolmkahora@gmail.com}} ~ 
    \href{https://linkedin.com/in/malcolm-kahora/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/malcolm-kahora}}  ~
    \href{https://github.com/k-kahora}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/k-kahora}}
    \vspace{-8pt}
\end{center}

% Date
\vspace{12pt}
\today

%% % Addressee
%% \vspace{12pt}
%% Hiring Manager\\
%% Door Dash\\
%% Door Dash Adress\\
%% California\\

% Opening
\vspace{12pt}
Dear Hiring Manager,

% Body
\vspace{12pt}
One of my teachers made me aware of this position via email, she sent a email with link to Steven Pungdumri linkedin post where he presented a some newgrad positions at door dash it caught my interest.  I am writing to express my interest in the Software Engineer at DoorDash, as advertised on Linked in sent from my professor. With a Bachelor of Science in Computer Science from The College of New Jersey and hands-on experience in Software Engineering, I am confident in my ability to contribute effectively to your team.

I have a previous internship with Northwestern Mutual software engineering, I learned data bases in one of my classes.  Through developing software as a hobby I am able to have a good understanding of data structures and algorithms.  I have experience using python in my internship, however I have shifted my knowlege of programming in languages like python and java into languages I belive I would enjoy writing and learning ocaml as I was struggling to write complex python in part due to its lax type system.
I can learn new concepts very well, I have been using emacs since my freshmen year as well as dived into linux for the purpose of software developemnt and have been using nixos as my main operating system for several years at this point.  I truly enjoy looking at things from different perspectives and often treat programming as a recreational activity.  I also have been using version control as well as understodd its benifits long befor it was introduced in school, It gives me the heads up in collaboration as I am very familar with using it with additonal people.




B.S., M.S. in Computer Science or related disciplines with graduation date between Spring 2024 and Summer 2024
At least 2 previous Software Engineering internships or equivalent work experience, with no more than 2 years of full-time work experience
Experience working with databases (e.g. SQL)
Solid understanding of algorithms and data structures
Experience working with at least one object-oriented programming language )e.g. Python, Java, Kotlin, etc.)
Experience writing clean code, working with version control, and unit testing

 
%% [Paragraph 2: Experience and skills]
I have experience in 

%% [Paragraph 3: Why you're interested in this position/company]

% Closing
\vspace{12pt}
Thank you for considering my application. I am looking forward to the opportunity to further discuss how I can contribute to [Company Name]. Please feel free to contact me at 732-585-3225 or via email at malcolmkahora@gmail.com to schedule an interview.

\vspace{12pt}
Sincerely,

\vspace{50pt}
Malcolm Kahora

\end{document}
